---
title: "Homework 9"
author: "Matt Schwab"
date: "4/7/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Group Members: Matt Schwab

Repository Link: https://github.com/mschwab7/HW9.git
```{r}
av <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)
av
head(av)
View(av)
library(tidyverse)
av0 = av %>% filter(Name.Alias != "")
dim(av0)
(unique(av0$Name.Alias))
counter = av0 %>% group_by(Name.Alias) %>% summarise(name.count = n()) %>%
  arrange(desc(name.count))
view(counter)
av0 = av0 %>% filter(Name.Alias != "Vance Astrovik")
av1 = av0 %>% gather(key = time, value = death, c(11, 13, 15, 17, 19)) %>% 
  select(Name.Alias, time, death) %>%
  mutate(time = parse_number(time))
av2 = av0 %>% gather(key = time, value = return, c(12, 14, 16, 18, 20)) %>% 
  select(Name.Alias, time, return) %>%
  mutate(time = parse_number(time))
av.neat = left_join(av1, av2, by = c("Name.Alias", "time"))
view(av.neat)
unique(av.neat$Name.Alias)
```
#Validation

```{r}
view(av.neat)
death.count = av.neat %>% group_by(Name.Alias) %>% 
  summarise(Number.of.Deaths = sum(as.numeric(death == "YES")), 
            Number.of.Returns = sum(as.numeric(return == "YES"))) 
view(death.count)
dim(death.count)
dim(death.count %>% filter(Number.of.Deaths >0))
63/161

```
From the cleaned data, there are 161 total Avengers. 63 of them have died at least once. This is about 39.13%. We can say that approximately 40% of all members of the Avengers will die at least once.

```{r}
mcu9 = death.count %>% filter(Name.Alias %in% 
                                 c("Anthony Edward Stark", 
                                   "Robert Bruce Banner",
                                   "Steven Rogers",
                                   "Thor Odinson",
                                   "Clinton Francis Barton",
                                   "Natalia Alianovna Romanova",
                                   "Wanda Maximoff",
                                   "Pietro Maximoff",
                                   "Victor Shade (alias)"))
view(mcu9)
```

Of the 9 Avengers in the MCU movies, all of them have died at least once. Thor and Hawkeye have each died twice.

```{r}
Total.Deaths = sum(death.count$Number.of.Deaths)
Total.Deaths
Total.Returns = sum(death.count$Number.of.Returns)
Total.Returns
55/82
```
In the cleaned data, there are 82 total deaths. There were also 55 recoveries. This means that from any particular death, there is about a two-thirds chance that the Avenger would recover from it.

```{r}
sum(av0$Death1 == "YES")
sum(av0$Return1 == "YES")
sum(av0$Death2 == "YES")
sum(av0$Return2 == "YES")
sum(av0$Death3 == "YES")
sum(av0$Return3 == "YES")
44/63
8/15
```
From the cleaned data, there is about a 69.84% chance that an Avenger returns from their first death(44/63). There is about a 53.33% chance that an Avenger returns from their second death(8/15). There is about a 50% chance than an Avenger returns from their third death(1/2).

```{r}
view(death.count %>% filter(Name.Alias == "Jocasta"))
```

```{r}
(53/82)*12
(53/27) * 12
```
When considering the Avengers'53 year timeline at the time of the writing, a death occurs about once every 7.75 months. A permanent death occurs about once every 23.56 months.
